---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  background-color: #C4A287;
  color: #ffffff;
}
h2 {
  font-family: monospace;
  color: #ffffff;
}
a {
  font-size: 20px;
  font-family: monospace;
  color: #ffffff;
}
```


```{r}
library(tidyverse)

csv_file <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTQQfD4SXVDzkoOutafvWrCrF2fGRa33qoL5KE_wvvTEaCqyCAzmTJqoybDdfMXNoXkcY5S0kqdCPr4/pub?output=csv"

logged_data <- read_csv(csv_file) 

latest_data <- logged_data %>% 
  rename(temperature_feel = 2,
         battery_percentage = 3,
         did_you_eat_past_hour = 4,
         meal_count = 5)


avr_battery <- mean(latest_data$battery_percentage)

lowest_battery <- min(latest_data$battery_percentage)

avr_meal_count <- mean(latest_data$meal_count, na.rm = TRUE)

highest_meal_count <- max(latest_data$meal_count, na.rm = TRUE)


ggplot(data = latest_data) +
  geom_bar(aes(x = temperature_feel, fill = temperature_feel)) + 
  labs(title = "How was the temperature for you?", 
       subtitle = "Comparing the feel of the temperatures at different times",
       x = "How does the temperature feel like for you?", 
       y = "Number of responses")

ggplot(data = latest_data) +
  geom_bar(aes(x = did_you_eat_past_hour, fill = did_you_eat_past_hour)) +
  labs(title = "Did you eat anytime during the past hour?", 
       subtitle = "Comparing when I ate during the past hour at different times",
       x = "Did you eat anytime at the past hour?", 
       y = "Number of responses")



```

## Temperature feel and hourly eating activity

For this report, I wanted to see what my status is throughout the day. I measured this through many variables such as my battery phone percentage, the meal count for today, and so on. For the graphs, I have used two different variables. One is temperature feel (which measures how I felt about the temperature around me generally), as well as my hourly eating activity (This variable shows how many times I have eaten in the past hour when answering the survey). 

From the survey, I was able to make dynamic graphs out of two variables (temperature feel and hourly eating activity). For the variable "temperature_feel", we can see how most of the responses is "Just right". 
And for the variable "did_you_eat_past_hour", we can see how the graph is even on both sides (10 "no" responses and 10 "yes" responses). 

I was also able to collect data from my other variables (such as battery phone percentage and meal count). Aside from the dynamic graphs, I found out that in the 20 occasions I've answered the survey, the average(mean) battery percentage of my phone is `r avr_battery`%. While the lowest data point recorded for battery percentage is `r lowest_battery`%. For meal count, in all occasions I answered the survey, I have had around `r avr_meal_count` on average. And the most meals I have had when answering the survey is `r highest_meal_count`.
